Zero-shot task adaptation by meta-mapping from task to task

### 2019-09-04 writing/embedded_meta_learning_appendix.tex
Tweaks, continual -> appendix, continuing reframing

\appendix
The supplemental material is organized as follows: In section \ref{app_clarifying_meta_mapping} we clarify some definitional details, and discuss the value of meta-mappings in detail by comparing to other methods of performing a new task. In section \ref{app_supp_figures} we provide supplemental figures. In section \ref{app_cards_tsne} we show $t$-sne results for the cards domain. In section \ref{app_lesion_results} we provide some lesion studies. In section \ref{app_detailed_methods} we list details fo the datasets and architectures we used, as well as providing links to the source code for all models, experiments, and analyses. In section \ref{app_numerical_results} we provide means and bootstrap CIs corresponding to the major figures in the paper. \par

@@

>>>>

\appendix
The supplemental material is organized as follows: In section \ref{app_clarifying_meta_mapping} we clarify some definitional details, and discuss the value of meta-mappings in detail by comparing to other methods of performing a new task. In section 
\ref{app_continual} we describe a continual-learning like perspective based on our approach. In section \ref{app_supp_figures} we provide supplemental figures. In section \ref{app_cards_tsne} we show $t$-sne results for the cards domain. In section \ref{app_lesion_results} we provide some lesion studies. In section \ref{app_detailed_methods} we list details fo the datasets and architectures we used, as well as providing links to the source code for all models, experiments, and analyses. In section \ref{app_numerical_results} we provide means and bootstrap CIs corresponding to the major figures in the paper. \par

@@

\section{Continual learning} \label{app_continual}
\includegraphics[width=\textwidth]{figures/continual/continual_learning.png}
\caption{Once the meta-learning system has been trained on a distribution of prior tasks, its performance on new tasks can be tuned by caching its guessed embeddings for the tasks and then optimizing those, thus avoiding any possibility of interfering with performance on prior tasks. Starting from random embeddings in the trained model results in slower convergence, while in an untrained model the embeddings cannot be optimized well. Error-bars are bootstrap 95\%-CIs.}
\label{poly_continual_results}
\vspace{-0.7em}
\paragraph{Continual learning:} Although the meta-learning approach is effective for rapidly adapting to a new task, it is unreasonable to think that our system must consider every example it has seen at each inference step. We would like to be able to store our knowledge more efficiently, and allow for further refinement. Furthermore, we would like the system to be able to adapt to new tasks (for which its guessed solution isn't perfect) without catastrophically interfering with prior tasks \citep{McCloskey1989}. \par
A very simple solution to these problems is naturally suggested by our architecture. Specifically, task embeddings can be cached so that they don't have to be regenerated at each inference step. This also allows optimization of these embeddings without altering the other parameters in the architecture, thus allowing fine-tuning on a task without seeing more examples, and without interfering with performance on any other task \citep[cf.][]{Rumelhart1993, Lampinen2018a}. This is like the procedure of \citet{Rusu2019}, except considered across episodes. That is, we can see the meta-learning step as a ``warm start'' for an optimization procedure over embeddings that are cached in memory \citep[cf.][]{Kumaran2016}. While this is not a traditional continual learning perspective, we think it provides an interesting perspective on the issue. It might in fact be much more memory-efficient to store an embedding per task, compared to storing an extra ``importance'' parameter for every parameter in our model, as in e.g. elastic weight consolidation \citep{Kirkpatrick2016}. It also provides a stronger guarantee of non-interference. \par
To test this idea, we pre-trained the system on 100 polynomial tasks, and then introduced 100 new tasks. We trained on these new tasks by starting from the meta-network's ``guess'' at the correct task embedding, and then optimizing this embedding without altering the other parameters. The results are shown in fig. \ref{poly_continual_results}. The meta-network embeddings offer good immediate performance, and substantially accelerate the optimization process, compared to a randomly-initialized embedding (see supp. fig. \ref{supp_poly_continual_results} for a more direct comparison). Furthermore, this ability to learn is due to training, not simply the expressiveness of the architecture, as is shown by attempting the same with an untrained network. \par

### 2019-09-04 writing/embedded_meta_learning_main.tex
Tweaks, continual -> appendix, continuing reframing

\section{Extensions}

@@

\paragraph{Language:} Language is a fundamental piece of human flexibility, and we would be remiss to ignore it. In many of the intuitive illustrations we've given, the examples of the meta-mapping are implicit in your prior knowledge about the world. For example, ``try to lose at go'' does not give explicit examples of the ``lose'' meta-mapping, but rather relies on prior knowledge of what losing means. This is a much more efficient way to achieve zero-shot performance on a new losing task. In order to replicate this, we trained the EML system with both meta-mappings based on examples, and meta-mappings based on language. In the language-based meta-mappings, a language input identifying the meta-mapping (but not the basic task to apply it to) is provided to the network. This language input is encoded by a language encoder, and then provided as input to $\mathcal{H}$ instead of the output of $\mathcal{M}$. The meta-mapping then proceeds as normal --- $\mathcal{H}$ parameterizes $F$, which is used to transform the embedding of the input task to produce an embedding for the target task. \par

@@

\includegraphics[width=\textwidth]{figures/continual/continual_learning.png}
\caption{Once the meta-learning system has been trained on a distribution of prior tasks, its performance on new tasks can be tuned by caching its guessed embeddings for the tasks and then optimizing those, thus avoiding any possibility of interfering with performance on prior tasks. Starting from random embeddings in the trained model results in slower convergence, while in an untrained model the embeddings cannot be optimized well. Error-bars are bootstrap 95\%-CIs.}
\label{poly_continual_results}
\paragraph{Continual learning:} Although the meta-learning approach is effective for rapidly adapting to a new task, it is unreasonable to think that our system must consider every example it has seen at each inference step. We would like to be able to store our knowledge more efficiently, and allow for further refinement. Furthermore, we would like the system to be able to adapt to new tasks (for which its guessed solution isn't perfect) without catastrophically interfering with prior tasks \citep{McCloskey1989}. \par
A very simple solution to these problems is naturally suggested by our architecture. Specifically, task embeddings can be cached so that they don't have to be regenerated at each inference step. This also allows optimization of these embeddings without altering the other parameters in the architecture, thus allowing fine-tuning on a task without seeing more examples, and without interfering with performance on any other task \citep[cf.][]{Rumelhart1993, Lampinen2018a}. That is, we can see the meta-learning step as a ``warm start'' for an optimization procedure over embeddings that are cached in memory \citep[cf.][]{Kumaran2016}.\footnote{Note that the weights generated by the hyper network could be cached instead of the embeddings, which would be much more memory intensive but would allow even better tuning and would not require passing through the hyper network at inference time.} While this is not a traditional continual learning perspective, we think it provides an interesting perspective on the issue.\par 
To test this idea, we pre-trained the system on 100 polynomial tasks, and then introduced 100 new tasks. We trained on these new tasks by starting from the meta-network's ``guess'' at the correct task embedding, and then optimizing this embedding without altering the other parameters. The results are shown in fig. \ref{poly_continual_results}. The meta-network embeddings offer good immediate performance, and substantially accelerate the optimization process, compared to a randomly-initialized embedding (see supp. fig. \ref{supp_poly_continual_results} for a more direct comparison). Furthermore, this ability to learn is due to training, not simply the expressiveness of the architecture, as is shown by attempting the same with an untrained network. \par 

@@

\paragraph{Related work:} Our work is an extrapolation from the rapidly-growing literature on meta-learning \citep[e.g.][]{Vinyals2016, Santoro2016, Finn2017a, Finn2018, Stadie2018, Botvinick2019}. It is also related to the literature on continual learning, or more generally tools for avoiding catastrophic interference based on changes to the architecture \citep[e.g.][]{Fernando2017, Rusu2016}, loss \citep[e.g.][]{Kirkpatrick2016, Zenke2017, Aljundi2019}, or external memory \citep[e.g.][]{Sprechmann2018}. Recent work has also begun to blur the separation between these approaches, for example by meta-learning in an online setting \citep{Finn2019}. Our work is specifically inspired by the algorithms that attempt to have the system learn to adapt to a new task via activations rather than weight updates, either from examples \citep[e.g.][]{Wang2016a, Duan2016}, or a task input \citep[e.g.][]{Borsa2019}. \par

@@

There has also been other recent interest in task (or function) embeddings. In simultaneous work Achille et al. \citep{Achille2019} proposed computing embeddings for visual tasks from the Fisher information of the parameters in a model partly tuned on the task. They show that this captures some interesting properties of the tasks, including some types of semantic relationships, and can help identify models that can perform well on a task. Rusu and colleagues recently suggested a similar meta-learning framework where latent codes are computed for a task which can be decoded to a distribution over parameters \citep{Rusu2019}. Other recent work has tried to learn representations for skills \citep[e.g.][]{Eysenbach2019} or tasks \citep[e.g.]{Hsu2019} for exploration and representation learning. Our perspective can be seen as a generalization of these that learns task embeddings in an end-to-end way, allows parameterizing a model (while some approaches only allow selection), but most importantly allows for remapping of behavior by meta-tasks. To the best of our knowledge none of the prior work has explored meta-mappings. \par

@@

In this paper, we've highlighted a new type of flexibility in the form of meta-mapping -- mapping between tasks. We've suggested that achieving this type of flexibility is difficult in most deep learning architectures, because they separate computation from the knowledge of what is being computed. To address this, we've proposed explicitly representing tasks by function embeddings, and deriving the computation from these embeddings via a HyperNetwork. This allows transformations over task embeddings to transform the system's behavior. This is analogous to how transformations over data perform basic tasks. Following this analogy, we've proposed a meta-learning system which takes a functional perspective, embeds tasks and data into a shared latent space, and then meta-learns to make basic- and meta-mappings over this space. The requisite meta-task sample complexity is small; we showed generalization to unseen meta-mappings after training on only 20 meta-mappings.\par
We see our proposal as a logical progression from the fundamental idea of meta-learning -- that there is a continuum between data and tasks. This naturally leads to the idea of manipulating task representations just like we manipulate data. We've shown that this approach yields considerable flexibility, most importantly the meta-mapping ability to adapt zero-shot to a new task. We've also shown that our approach provides a useful perspective on continual learning. We hope that these results will lead to the development of more powerful and flexible deep-learning models. \par

>>>>

\section{An extension via language}

@@

Language is a fundamental piece of human flexibility, and we would be remiss to ignore it. In many of the intuitive illustrations we've given, the examples of the meta-mapping are implicit in your prior knowledge about the world. For example, ``try to lose at go'' does not give explicit examples of the ``lose'' meta-mapping, but rather relies on prior knowledge of what losing means. This is a much more efficient way to achieve zero-shot performance on a new losing task. In order to replicate this, we trained the EML system with both meta-mappings based on examples, and meta-mappings based on language. In the language-based meta-mappings, a language input identifying the meta-mapping (but not the basic task to apply it to) is provided to the network. This language input is encoded by a language encoder, and then provided as input to $\mathcal{H}$ instead of the output of $\mathcal{M}$. The meta-mapping then proceeds as normal --- $\mathcal{H}$ parameterizes $F$, which is used to transform the embedding of the input task to produce an embedding for the target task. \par

@@

@@

\paragraph{Related work:} Our work is an extrapolation from the rapidly-growing literature on meta-learning \citep[e.g.][]{Vinyals2016, Santoro2016, Finn2017a, Finn2018, Stadie2018, Botvinick2019}. It is also related to the literature on continual learning, or more generally tools for avoiding catastrophic interference based on changes to the architecture \citep[e.g.][]{Fernando2017, Rusu2016}, loss \citep[e.g.][]{Kirkpatrick2016, Zenke2017, Aljundi2019}, or external memory \citep[e.g.][]{Sprechmann2018}. We also connect to a different perspective on continual learning in appendix \ref{app_continual}. Recent work has also begun to blur the separation between these approaches, for example by meta-learning in an online setting \citep{Finn2019}. Our work is specifically inspired by the algorithms that attempt to have the system learn to adapt to a new task via activations rather than weight updates, either from examples \citep[e.g.][]{Wang2016a, Duan2016}, or a task input \citep[e.g.][]{Borsa2019}. \par

@@

There has also been other recent interest in task (or function) embeddings. Achille et al. \citep{Achille2019} recently proposed computing embeddings for visual tasks from the Fisher information of the parameters in a model partly tuned on the task. They show that this captures some interesting properties of the tasks, including some types of semantic relationships, and can help identify models that can perform well on a task. Rusu and colleagues recently suggested a similar meta-learning framework where latent codes are computed for a task which can be decoded to a distribution over parameters \citep{Rusu2019}. Other recent work has tried to learn representations for skills \citep[e.g.][]{Eysenbach2019} or tasks \citep[e.g.]{Hsu2019} for exploration and representation learning. Our perspective can be seen as a generalization of these that allows for remapping of behavior by meta-tasks. To the best of our knowledge none of the prior work has explored meta-mappings, and therefore it has not allowed for zero-shot performance of a new task. \par

@@

In this paper, we've highlighted a new type of flexibility in the form of meta-mapping -- mapping between tasks. Meta-mapping can produce zero-shot performance on novel tasks, based on their relationship to old tasks. However, achieving this type of flexibility is difficult in architectures that separate computation from the knowledge of what is being computed. To address this, our EML architecture explicitly represents tasks by function embeddings, and derives the computation from these embeddings via a HyperNetwork. This allows for our key insight: using transformations over task embeddings to transform the system's behavior. This is analogous to how transformations over data perform basic tasks. Following this analogy, we've proposed a meta-learning system which takes a functional perspective, embeds tasks and data into a shared latent space, and then meta-learns to make basic- and meta-mappings over this space. The requisite meta-task sample complexity is small; we showed generalization to unseen meta-mappings after training on only 20 meta-mappings. That is, we are able to achieve zero-shot performance on a novel task based on a relationship between tasks that was never trained on. This is a step closer to human-level flexibility.\par
We see our proposal as a logical progression from the fundamental idea of meta-learning -- that there is a continuum between data and tasks. This naturally leads to the idea of manipulating task representations just like we manipulate data. We've shown that this approach yields considerable flexibility, most importantly the meta-mapping ability to adapt zero-shot to a new task. We hope that these results will lead to the development of more powerful and flexible deep-learning models. \par
